Online analysis supplement

### 2021-11-10 index.Rmd
Way more models.

```{r}
pa <- gbd %>% 
  ggplot(aes(year, val, group = country, col = region)) +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .5) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )
pb <- gbd %>% 
  mutate(Group = str_glue("{sex} ({age})")) %>% 
  ggplot(aes(year, val, col = Group)) +
  scale_color_brewer(palette = "Paired") +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    "Year",
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .6) +
  facet_grid(cause~region, scales = "free_y")

@@

# Calculate random demographics time effects
random_effects %>% 
  mutate(
    `Male (20 to 24)` = time + `time:sex1`*.5 + `time:sex1:age1`*.25
  )

pivot_longer(
    c(`(Intercept)`:`time:sex1:age1`, `Male (20 to 24)`:`Female (15 to 19)`), 
    names_to = "Parameter", 
    values_to = "Coefficient"
    )

bind_rows(
  fixed_effects,
  fixed_effects_demographics, 
  .id = "Type"
) %>% 
  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
  mutate(Parameter = fct_inorder(Parameter)) %>%
  mutate(cause = factor(cause)) %>% 
  rowwise() %>% 
  mutate(
    sig = factor(
      !between(0, CI_low, CI_high), 
      levels = c(TRUE, FALSE)
    )
  ) %>% 
  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
  scale_color_discrete(
    "Outcome"
  ) +
  scale_x_continuous(
    "Estimate (95%CI)"
  ) +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = 0, size = .2, alpha = .2) +
  geom_point(
    data = random_effects %>% 
      filter(cluster == "country"), 
    shape = 1, size = .15, alpha = .2,
    position = position_dodge2v(.5)
    ) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodge2v(.5),
    fill = "white", size = .3, fatten = 5
  ) +
  guides(shape = "none") +
  facet_wrap("Type", ncol = 2, scales = "free") +
  theme(axis.title.y = element_blank())
```

@@

```{r fit-gbd-time-brms, eval = FALSE}
# bf_gbd_time <- bf(
#   mvbind(
#     val_Depression,
#     val_Anxiety,
#     val_Self_harm
#   ) ~ 1 + Time +
#     (1 + Time || region) +
#     (1 + Time || country)
# ) +
#   set_rescor(FALSE)
# 
# fit_gbd_time <- brm(
#   bf_gbd_time,
#   gbd_y_w,
#   file = "output/brm-gbd-time-mv",
#   chains = 5,
#   cores = 5,
#   iter = 300, warmup = 150, refresh = 10,
#   threads = 2,
#   control = list(adapt_delta = .9, max_treedepth = 15)
# )

bf_gbd_time_demos <- bf(
  mvbind(
    Depression,
    Anxiety,
    Selfharm
  ) ~ 1 + Time * Sex * Age +
    (1 + Time * Sex * Age || region) +
    (1 + Time * Sex * Age || country)
) +
  set_rescor(FALSE)

p <- prior(normal(0, 1), class = b, resp = Anxiety) +
  prior(normal(0, 1), class = b, resp = Depression) +
  prior(normal(0, 1), class = b, resp = Selfharm) +
  prior(student_t(7, 0, .5), class = sd, resp = Anxiety) +
  prior(student_t(7, 0, .5), class = sd, resp = Depression) +
  prior(student_t(7, 0, .5), class = sd, resp = Selfharm)

fit_gbd_time_demos <- brm(
  bf_gbd_time_demos,
  gbd_y_w,
  prior = p,
  file = "output/brm-gbd-time-mv-demos",
  chains = 5,
  cores = 5,
  iter = 250, warmup = 150, refresh = 10,
  threads = 2,
  control = list(adapt_delta = .9, max_treedepth = 15)
)
```

##### Plot: Average effects of time

@@

bf_gbd_internet_demos <- bf(
  mvbind(
    Depression,
    Anxiety,
    Selfharm
  ) ~ 1 + Time * Sex * Age + i1_cw * Sex * Age + i1_cb +
    (1 + Time * Sex * Age + i1_cw * Sex * Age || region) +
    (1 + Time * Sex * Age + i1_cw * Sex * Age || country)
) +
  set_rescor(FALSE)

p <- prior(normal(0, 1), class = b, resp = Anxiety) +
  prior(normal(0, 1), class = b, resp = Depression) +
  prior(normal(0, 1), class = b, resp = Selfharm) +
  prior(student_t(7, 0, .5), class = sd, resp = Anxiety) +
  prior(student_t(7, 0, .5), class = sd, resp = Depression) +
  prior(student_t(7, 0, .5), class = sd, resp = Selfharm)

fit_gbd_internet_demos <- brm(
  bf_gbd_internet_demos,
  gbd_y_w,
  prior = p,
  file = "output/brm-gbd-internet-mv-demos",
  chains = 5,
  cores = 5,
  iter = 250, warmup = 150, refresh = 10,
  threads = 2,
  control = list(adapt_delta = .9, max_treedepth = 15)
)
```

>>>>

```{r eval = FALSE}
pa <- gbd %>% 
  ggplot(aes(year, val, group = country, col = region)) +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .5) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )
pb <- gbd %>% 
  mutate(Group = str_glue("{sex} ({age})")) %>% 
  ggplot(aes(year, val, col = Group)) +
  scale_color_brewer(palette = "Paired") +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    "Year",
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .6) +
  facet_grid(cause~region, scales = "free_y")

@@

bind_rows(
  fixed_effects,
  fixed_effects_demographics, 
  .id = "Type"
) %>% 
  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
  mutate(Parameter = fct_inorder(Parameter)) %>%
  mutate(cause = factor(cause)) %>% 
  rowwise() %>% 
  mutate(
    sig = factor(
      !between(0, CI_low, CI_high), 
      levels = c(TRUE, FALSE)
    )
  ) %>% 
  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
  scale_color_discrete(
    "Outcome"
  ) +
  scale_x_continuous(
    "Estimate (95%CI)"
  ) +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = 0, size = .2, alpha = .2) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodge2v(.5),
    fill = "white", size = .3, fatten = 5
  ) +
  guides(shape = "none") +
  facet_wrap("Type", ncol = 2, scales = "free") +
  theme(axis.title.y = element_blank())
```

@@

correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix

note we use beta so transform edge values

we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow

##### Time: Main effects

We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.

$$
\begin{align*}
y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\

\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
  \beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\

i_{i[c][r]} &\sim 
  \text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\

\mu^i_{i[c][r]} &= \text{logit}(
  \beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
  \beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\

\left[\begin{array}{c}
\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
\end{array}\right] 
&\sim MVN(
\left[\begin{array}{c}
0 \\ 0 \\ 0 \\ 0
\end{array}\right],
\Sigma^c
),

\left[\begin{array}{c}
\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
\end{array}\right] 
\sim MVN(
\left[\begin{array}{c}
0 \\ 0 \\ 0 \\ 0
\end{array}\right],
\Sigma^r
)
\end{align*}
$$

```{r}
# Transform edge proportions to fit beta distribution
gbd_10 <- gbd_wide %>% 
  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
  mutate(internet = if_else(internet == 1, .9999999999, internet))

# Define a model of internet proportion over time
bf_int <- bf(
  internet ~ 1 + time + 
    (1 + time |c| country) +
    (1 + time |r| region), 
  family = Beta()
)

# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)

bf_time_mv <- bf(
  mvbind(Depression, Anxiety, Selfharm) ~ 
    1 + time +
    (1 + time |c| country) +
    (1 + time | region),
  family = gaussian()
) +
  bf_int +
  set_rescor(FALSE)

# Fit models in background (need 12 cores)
file_path <- "brm-time-main-effects"
if (!file.exists(file_path)) {
  job::job({
    fit_anx <- brm(
      bf_int + bf_anx + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-anxiety",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms anxiety")
  job::job({
    fit_dep <- brm(
      bf_int + bf_dep + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-depression",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms depression")
  fit_sel <- brm(
    bf_int + bf_sel + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-selfharm",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
  fits_brm_time_main <- tibble(
    outcome = c("Anxiety", "Depression", "Selfharm"),
    fit = list(fit_anx, fit_dep, fit_sel)
  )
  write_rds(fits_brm_time_main, file_path)
} else {fits_brm_time_main <- read_rds(file_path)}
```

##### Time: Interactions

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time * sex + time * age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)

# Fit models
file_path <- "brm-time-interactions"
if (!file.exists(file_path)) {
  job::job({
    fit_anx <- brm(
      bf_int + bf_anx + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-anxiety-int2",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms anxiety")
  job::job({
    fit_dep <- brm(
      bf_int + bf_dep + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-depression-int2",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms depression")
  fit_sel <- brm(
    bf_int + bf_sel + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-selfharm-int2",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
  fits_brm_time_interactions <- tibble(
    outcome = c("Anxiety", "Depression", "Selfharm"),
    fit = list(fit_anx, fit_dep, fit_sel)
  )
  write_rds(fits_brm_time_interactions, file_path)
} else {fits_brm_time_interactions <- read_rds(file_path)}
```

Model comparison using waic shows that interactive model is favored across the board.

```{r eval = FALSE}
waics <- left_join(
  rename(fits_brm_time_main, fit_main = fit),
  rename(fits_brm_time_interactions, fit_intr = fit)
) %>% 
  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
waics$waic[[3]]
```

Show main effects

```{r}
# Fixed effects parameters
fixed_effects <- fits_brm_time_interactions %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  filter(
    Effects == "fixed", 
    Parameter != "(Intercept)"
  ) 
# Fixed effects per demographic
fixed_effects_demographics <- fits_brm_time_interactions %>% 
  mutate(
    out = map2(
      fit, outcome,
      ~emtrends(
        .x, 
        var = "time", 
        by = c("sex", "age"), 
        resp = .y
      ) %>% 
        parameters() %>% 
        as.data.frame()
    )
  )
fixed_effects_demographics %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  mutate(Parameter = str_glue("{sex}\n({age})"))

bind_rows(
  fixed_effects,
  fixed_effects_demographics, 
  .id = "Type"
) %>% 
  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
  mutate(Parameter = fct_inorder(Parameter)) %>%
  mutate(cause = factor(cause)) %>% 
  rowwise() %>% 
  mutate(
    sig = factor(
      !between(0, CI_low, CI_high), 
      levels = c(TRUE, FALSE)
    )
  ) %>% 
  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
  scale_color_discrete(
    "Outcome"
  ) +
  scale_x_continuous(
    "Estimate (95%CI)"
  ) +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = 0, size = .2, alpha = .2) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodge2v(.5),
    fill = "white", size = .3, fatten = 5
  ) +
  guides(shape = "none") +
  facet_wrap("Type", ncol = 2, scales = "free") +
  theme(axis.title.y = element_blank())
```

```{r}
library(modelbased)
x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
tmp <- fits_brm %>% 
  mutate(
    # Average effect
    avg = map2(
      fit, 
      Outcome, 
      ~hypothesis(.x, str_glue("{.y}_time = 0"))
    ),
    # By country effect
    by_country = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "country"
      )
    ),
    # By region effect
    by_region = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "region"
      )
    )
  ) %>% 
  select(-fit)

tmp %>% 
  select(Outcome, avg) %>% 
  mutate(avg = map(avg, ))

tmp$by_region[[1]] %>% str

##### Internet: Main effects

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time + sex + age + i1_cw + i1_cb +
    (1 + time + sex + age + i1_cw |c| country) +
    (1 + time + sex + age + i1_cw |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + i1_cw + i1_cb +
    (1 + time + sex + age + i1_cw |c| country) +
    (1 + time + sex + age + i1_cw |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + i1_cw + i1_cb + 
    (1 + time + sex + age + i1_cw |c| country) +
    (1 + time + sex + age + i1_cw |r| region),
  family = gaussian()
)

# Fit models in background (need 12 cores)
job::job({
  fit_anx <- brm(
    bf_int + bf_anx + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-internet-anxiety",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms anxiety")
job::job({
  fit_dep <- brm(
    bf_int + bf_dep + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-internet-depression",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms depression")
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-selfharm",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
```

##### Internet: Interactions

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  family = gaussian()
)

# Fit models in background (need 12 cores)
job::job({
  fit_anx <- brm(
    bf_anx,
    data = gbd_wide,
    file = "output/brm-gbd-time-internet-anxiety-int2",
    chains = 4,
    cores = 4,
    iter = 1200, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms anxiety")
job::job({
  fit_dep <- brm(
    bf_dep,
    data = gbd_wide,
    file = "output/brm-gbd-time-internet-depression-int2",
    chains = 4,
    cores = 4,
    iter = 1200, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms depression")
fit_sel <- brm(
  bf_sel,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
```

###### Plot: Average effects of time

@@

bf_gbd_internet_demos <- bf(
  mvbind(
    Depression,
    Anxiety,
    Selfharm
  ) ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
    (1 + time * sex * age + i1_cw * sex * age | country)
) +
  set_rescor(FALSE)

p <- prior(normal(0, 3), class = b, resp = Anxiety) +
  prior(normal(0, 3), class = b, resp = Depression) +
  prior(normal(0, 3), class = b, resp = Selfharm) +
  prior(student_t(7, 0, 1), class = sd, resp = Anxiety) +
  prior(student_t(7, 0, 1), class = sd, resp = Depression) +
  prior(student_t(7, 0, 1), class = sd, resp = Selfharm)

job::job({fit_gbd_internet_demos <- brm(
  bf_gbd_internet_demos,
  gbd_wide,
  prior = p,
  file = "output/brm-gbd-internet-mv-demos",
  chains = 5,
  cores = 5,
  iter = 450, warmup = 300, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9, max_treedepth = 15)
)}, title = "brms internet")
```
